Gammapy: A Python package for gamma-ray astronomy

### 2022-10-24 src/ms-review.tex
Update src/ms-review.tex
Co-authored-by: Bruno Khélifi <khelifi@in2p3.fr>

The Jupyter notebooks tutorials are stored stripped of their output cells,
which greatly helps in identifying differences in the contribution review.
During the CI these are executed, the output cells parsed and, in case an error
is found in one of the output cells then validation fails. Code formatting of
the input cells is also done, parsing their content and using a particular
syntax to provide links to the API documentation pages. The resulting web
published tutorials also provide links to playground spaces in
myBinder~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
on-line in versioned virtual environments hosted in the myBinder
infrastructure. Users may also play with the tutorials locally in their
laptops. They can download a specific version of the tutorials together with
the associated datasets needed and the specific conda computing environment,
using the \textit{gammapy download} command.

>>>>

The Jupyter notebooks tutorials are stored stripped of their output cells,
which greatly helps in identifying differences in the contribution review.
During the CI these are executed, the output cells parsed and, in case an error
is found in one of the output cells then validation fails. Code formatting of
the input cells is also done, parsing their content and using a particular
syntax to provide links to the API documentation pages. The resulting web
published tutorials also provide links to playground spaces in
"myBinder"~\citep{project_jupyter-proc-scipy-2018}, where they may be executed
on-line in versioned virtual environments hosted in the myBinder
infrastructure. Users may also play with the tutorials locally in their
laptops. They can download a specific version of the tutorials together with
the associated datasets needed and the specific conda computing environment,
using the \textit{gammapy download} command.
